Attack Graph Generation for Microservice Architecture

### 2018-11-27 paper_own_docker/chapters/evaluation.tex
Minor comments from reviewer 2 fixed

Modern microservice architectures use many different technologies,  different numbers of containers, various degrees of connectivity, and have different numbers of vulnerabilities. Therefore, it is critically important to demonstrate that an attack graph generator works well in such heterogeneous scenarios. Here, we tested the proposed system on real and slightly modified GitHub examples (Table \ref{table_technologies}). We employed test examples that are publicly available to facilitate potential future comparison characterized by different system properties (e.g., topologies, technologies and vulnerabilities) and different usage domains. We also had to consider the fact that an overwhelming majority of publicly-available examples are small, i.e., only one or a few containers, which made finding appropriate test examples challenging. The resulting examples are as follows: NetflixOSS, the Atsea Sample Shop App, and the JavaEE demo. NetflixOSS is a microservice system provided by Netflix comprising 10 containers and uses many tools, e.g., Spring Cloud, Netflix Ribbon, and Netflix Eureka. The Atsea Sample Shop App is an e-commerce sample web application comprising four containers and uses Spring Boot, React, NGINX, and PostgreSQL. The JavaEE demo is a sample application for browsing movies comprising only two containers and uses JavaEE, React, and Tomcat EE. We ran the attack graph generator and manually verified the resulting attack graphs for the small examples based on domain knowledge under the assumption that the output from Clair, the NVD attack vectors \cite{booth2013national}, and the preconditions and postconditions from Aksu et al. \cite{aksu2018automated} are \textit{correct}. After running the proposed attack graph generator, the attack graphs for the Atsea Sample Shop App and JavaEE demo were small as expected, containing only a few nodes and edges. The structure of the NetflixOSS attack graph demonstrated a nearly linear structure in which each node was connected to a small number of other nodes to form a chain of attacks. This linearity is due to the fact that each container is connected to only a few other containers to reduce unnecessary communication and increase encapsulation. Therefore, based on this degree of connectivity, an attacker needs to perform multiple intermediate steps to reach the target container. Note that all examples terminated, there were no directed edges from containers with higher privileges to lower privileges, no duplication of nodes, and no reflexive edges were observed, which is in line with the monotonicity property. In addition, the run time of the proposed system with each example was short, however, additional scalability tests were required. Therefore, the Phpmailer and Samba system was extended and employed as an artificial example to perform scalability tests. This is discussed in the following subsection.

>>>>

Modern microservice architectures use many different technologies,  different numbers of containers, various degrees of connectivity, and have different numbers of vulnerabilities. Therefore, it is critically important to demonstrate that an attack graph generator works well in such heterogeneous scenarios. Here, we tested the proposed system on real and slightly modified GitHub examples (Table \ref{table_technologies}). We employed test examples that are publicly available to facilitate potential future comparison characterized by different system properties (e.g., topologies, technologies and vulnerabilities) and different usage domains. We also had to consider the fact that an overwhelming majority of publicly-available examples are small, i.e., only one or a few containers, which made finding appropriate test examples challenging. The resulting examples are as follows:

\begin{itemize}
	\item NetflixOSS is a microservice system provided by Netflix comprising 10 containers and uses many tools, e.g., Spring Cloud, Netflix Ribbon, and Netflix Eureka.
	\item The Atsea Sample Shop App is an e-commerce sample web application comprising four containers and uses Spring Boot, React, NGINX, and PostgreSQL.
	\item The JavaEE demo is a sample application for browsing movies comprising only two containers and uses JavaEE, React, and Tomcat EE.
\end{itemize}

   We ran the attack graph generator and manually verified the resulting attack graphs for the small examples based on domain knowledge under the assumption that the output from Clair, the NVD attack vectors \cite{booth2013national}, and the preconditions and postconditions from Aksu et al. \cite{aksu2018automated} are \textit{correct}. After running the proposed attack graph generator, the attack graphs for the Atsea Sample Shop App and JavaEE demo were small as expected, containing only a few nodes and edges. The structure of the NetflixOSS attack graph demonstrated a nearly linear structure in which each node was connected to a small number of other nodes to form a chain of attacks. This linearity is due to the fact that each container is connected to only a few other containers to reduce unnecessary communication and increase encapsulation. Therefore, based on this degree of connectivity, an attacker needs to perform multiple intermediate steps to reach the target container. Note that all examples terminated, there were no directed edges from containers with higher privileges to lower privileges, no duplication of nodes, and no reflexive edges were observed, which is in line with the monotonicity property. In addition, the run time of the proposed system with each example was short, however, additional scalability tests were required. Therefore, the Phpmailer and Samba system was extended and employed as an artificial example to perform scalability tests. This is discussed in the following subsection.

### 2018-11-27 paper_own_docker/chapters/method.tex
Minor comments from reviewer 2 fixed

In the preprocessing step, we use Clair to generate the vulnerabilities for a given image. Clair is a vulnerability scanner that inspects a Docker image and generates its vulnerabilities by providing a \textit{CVE-ID}, a description and an attack vector for each vulnerability. An attack vector is an entity that describes which conditions and effects are connected to the given vulnerability. We collect the fields in the attack vector as defined by the NVD \cite{booth2013national}, i.e., Access Vector (Local, Adjacent Network, Network), Access Complexity (Low, Medium, High), Authentication (None, Single, Multiple), Confidentiality Impact (None, Partial, Complete), Integrity Impact (None, Partial, Complete), and Availability Impact (None, Partial, Complete). Since Clair does not provide a command line interface to analyze a Docker image, we use Clairctl to analyze a complete Docker image.

>>>>

In the preprocessing step, we use Clair to generate the vulnerabilities for a given image. Clair is a vulnerability scanner that inspects a Docker image and generates its vulnerabilities by providing a \textit{CVE-ID}, a description and an attack vector for each vulnerability. An attack vector is an entity that describes which conditions and effects are connected to the given vulnerability. We collect the fields in the attack vector as defined by the NVD \cite{booth2013national}:

\begin{itemize}
	\item Access Vector (Local, Adjacent Network, Network)
	\item Access Complexity (Low, Medium, High)
	\item Authentication (None, Single, Multiple)
	\item Confidentiality Impact (None, Partial, Complete)
	\item Integrity Impact (None, Partial, Complete)
	\item Availability Impact (None, Partial, Complete)
\end{itemize}

Since Clair does not provide a command line interface to analyze a Docker image, we use Clairctl to analyze a complete Docker image.
